### 2023-02-26 manuscript.tex
Update README.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ad2c9cccb40e8cfde96b21bdb5c7368f051d42e5.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ad2c9cccb40e8cfde96b21bdb5c7368f051d42e5/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276977122

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6ddc6c567be38982e38bb2090b00fb76430b0776/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6ddc6c567be38982e38bb2090b00fb76430b0776}{SORTEE-Github-Hackathon/manuscript@6ddc6c5}
on February 26, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ad2c9cccb40e8cfde96b21bdb5c7368f051d42e5/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ad2c9cccb40e8cfde96b21bdb5c7368f051d42e5}{SORTEE-Github-Hackathon/manuscript@ad2c9cc}
on February 26, 2023.
